\hfill ~\\[-30mm] \phantom{h} \hfill\mbox{\small pre-print number if any?} \\[1cm] \vspace{13mm} \textbf{Precise predictions for same sign W-bosons scattering at the LHC}

### 2017-11-14 Draft/article.tex
fix of the affiliation

\date{}
\author{
Simon Brass$^{1\,}$,
Ansgar Denner$^{2\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4\,}$, \\
Alexander Karlberg$^{5\,}$, 
Mathieu Pellen$^{2\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{6\,}$,
Michael Rauch$^{7\,}$,
J\"urgen Reuter$^{8\,}$, \\
Vincent Rothe$^{8\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{8\,}$,
Marco Zaro$^{9\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^5$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
{\small\it
$^6$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        %
{\small\it
$^7$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^8$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^9$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]
        }

>>>>

\date{}
\author{
Simon Brass$^{1\,}$,
Ansgar Denner$^{2\,}$,
Stefan Dittmaier$^{3\,}$,
Michele Grossi$^{4,5\,}$, \\
Alexander Karlberg$^{6\,}$, 
Mathieu Pellen$^{2\,}$\footnote{E-mail:
  \texttt{mpellen@physik.uni-wuerzburg.de}},
Giovanni  Pelliccioli$^{7\,}$,
Michael Rauch$^{8\,}$,
J\"urgen Reuter$^{9\,}$, \\
Vincent Rothe$^{9\,}$, 
Christopher Schwan$^{3\,}$,
Pascal Stienemeier$^{9\,}$,
Marco Zaro$^{10\,}$\footnote{E-mail:
  \texttt{m.zaro@nikhef.nl}}.
\\[9mm]
{\small\it
$^1$Universit\"at Siegen, Department Physik,} \\ %
{\small\it Walter-Flex-Str.3, \linebreak %
        57068 Siegen, Germany}\\[3mm]
        %
{\small\it
$^2$Universit\"at W\"urzburg, %
        Institut f\"ur Theoretische Physik und Astrophysik,} \\ %
{\small\it Emil-Hilb-Weg 22, \linebreak %
        97074 W\"urzburg, %
        Germany}\\[3mm]
        %
$^3${\small\it
Albert-Ludwigs-Universit\"at Freiburg, Physikalisches Institut,} \\ %
{\small\it Hermann-Herder-Str.\ 3, \linebreak %
         79104 Freiburg, Germany}\\[3mm]
        %
{\small\it
$^4$Universit\'a di Pavia, Dipartimento di Fisica and INFN, Sezione di Pavia } \\ %
{\small\it Via A. Bassi 6, \linebreak %
        27100 Pavia, %
        Italy}\\[3mm]
%        
{\small\it
$^{5}$IBM Italia s.p.a.} \\ %
{\small\it Circonvallazione Idroscalo , \linebreak %
        20090 Segrate (MI), %
        Italy}\\[3mm]
        %
{\small\it
$^6$Department of Physics, University of Z\"urich,} \\ %
{\small\it CH-8057
Z\"urich, Switzerland}\\[3mm]
        %
$^7${\small\it
Universit\`a di Torino, Dipartimento di Fisica and INFN, Sezione di Torino } \\ %
{\small\it Via P. Giuria 1, \linebreak %
        10125 Torino, %
        Italy}\\[3mm]
        %
{\small\it
$^8$Institute for Theoretical Physics, Karlsruhe Institute of
Technology (KIT),} \\ %
{\small\it Karlsruhe, Germany}\\[3mm]
        %
{\small\it
$^9$DESY Theory Group,} \\ %
{\small\it Notkestr. 85, \linebreak %
        D-22607 Hamburg, Germany}\\[3mm]
        %
{\small\it
$^{10}$University X, %
        Institut Y,} \\ %
{\small\it Street X, \linebreak %
        XXXX city, %
        Country}\\[3mm]        
        }
